%
% File acl-hlt2011.tex
%
% Contact: gdzhou@suda.edu.cn
%%
%% Based on the style files for ACL2008 by Joakim Nivre and Noah Smith
%% and that of ACL2010 by Jing-Shin Chang and Philipp Koehn


\documentclass[11pt]{article}
\usepackage{acl-hlt2011}
\usepackage{adjustbox}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{multirow}
\usepackage{times}
\usepackage{url}
\usepackage{xcolor}

\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

\title{Large Scale Image Classification by Model Averaging}

\author{Jiao Chen \\
  Computer Science and Engineering\\
  {\tt chenjiao@msu.edu} \\\And
  Shaohua Yang\\
  Computer Science and Engineering\\
  {\tt yangshao@msu.edu} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
In our project, we apply multi-class SVM, Loggistic Regression and Neural network to classify the image samples that belong to 164 classes. We use machine learning tool Vowpal Wabbit (VW) to perform these three classification methods. VW is a online learning based tool, which provides reasonable classification accuracy and fast training and testing speed on large dataset. We tune the hyperparameters of these three classification models on part of our training dataset, and then train three classification models based on the whole training dataset. Overall, logistic regression achives an accuracy of 37.46\% on our testing data with 250,000 samples, while the accuracy of SVM is only 30.45\% on the same testing dataset. Neural network is much slower than SVM and logistic regression, but provides the highest accuracy (39.30\%) and MAP on our testing dataset. For evaluation, results of these three models are assembled together with equal weight. We get a evaluation MAP score of 72.81\%, which ranks first among 18 teams in this class.   
\end{abstract}


%\input{report_intro.tex}
%\input{report_prior.tex}
%\input{report_tables.tex}
\input{report_method.tex}
\input{report_result.tex}
%\input{report_discussion.tex}
%\input{report_conclusion.tex}


\clearpage
{\small
\bibliographystyle{acl}
\bibliography{references}
}


\end{document}
